---
params:
    save: NULL #"first.Rda"
    load: "first.Rda"
    completeReload: false
# bibliography: CohortDefinition.bib
# csl: nature-publishing-group-vancouver.csl
output:
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
    #citation_package: natbib
    #rticles::sim_article
fontsize: 11pt
geometry: margin=1in
classoptions: doublespace
longtable: true
header-includes:
  - \usepackage[numbers,sort&compress]{natbib}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{caption}
  - \usepackage{rotating}
  - \usepackage{multirow}
  - \usepackage{mwe,tikz}
  - \usepackage[percent]{overpic}
  - \usepackage{enumitem}
  - \usepackage{mas_fun}
  - \usepackage{hyperref}
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
library(tidyr)
library(xtable)
```

\centerline{{\Huge Results: Incidence}}

<!-- \captionsetup[table]{name=Supplementary Table} -->
<!-- \captionsetup[figure]{name=Supplementary Figure} -->
\captionsetup{labelfont=bf}

# Cohorts

```{r, echo=FALSE}
cohorts <- read.csv(file = system.file("settings", "CohortsToCreate.csv", package = "Covid19IncidenceRasInhibitors")) %>% select(cohortId, shinyName)

aceMonoId <- cohorts %>% filter(shinyName == "ACE mono") %>% select(cohortId) %>% pull()
arbMonoId <- cohorts %>% filter(shinyName == "ARB mono") %>% select(cohortId) %>% pull()
aceArbMonoId <- cohorts %>% filter(shinyName == "ACE/ARB mono") %>% select(cohortId) %>% pull()
ccbThzMonoId <- cohorts %>% filter(shinyName == "CCB/THZ mono") %>% select(cohortId) %>% pull()

aceComboId <- cohorts %>% filter(shinyName == "ACE +combo") %>% select(cohortId) %>% pull()
arbComboId <- cohorts %>% filter(shinyName == "ARB +combo") %>% select(cohortId) %>% pull()
aceArbComboId <- cohorts %>% filter(shinyName == "ACE/ARB +combo") %>% select(cohortId) %>% pull()
ccbThzComboId <- cohorts %>% filter(shinyName == "CCB/THZ +combo") %>% select(cohortId) %>% pull()

covidNarrowId <- cohorts %>% filter(shinyName == "COVID-19 narrow") %>% select(cohortId) %>% pull()

primaryAnalysisId <- 5 # Full stratified PS
```


# Sample sizes (monotherapy)

```{r, echo=FALSE, warning=FALSE, message=FALSE}

sidiapDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/SIDIAP"

dataFolder <- file.path(sidiapDir, "shinyData")
databaseId <- "SIDIAP"


# cmResults <- read.csv(file = file.path(sidiapDir, "cohort_method_result.csv")) 
cmResults <- readRDS(file = file.path(sidiapDir, "shinyData", paste0("cohort_method_result_", databaseId, ".rds")))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
  alpha <- 0.05
  power <- 0.8
  z1MinAlpha <- qnorm(1 - alpha/2)
  zBeta <- -qnorm(1 - power)
  pA <- cmResults$targetSubjects/(cmResults$targetSubjects + cmResults$comparatorSubjects)
  pB <- 1 - pA
  totalEvents <- abs(cmResults$targetOutcomes) + (cmResults$comparatorOutcomes)
  cmResults$mdrr <- exp(sqrt((zBeta + z1MinAlpha)^2/(totalEvents * pA * pB)))
  cmResults$targetYears <- cmResults$targetDays/365.25
  cmResults$comparatorYears <- cmResults$comparatorDays/365.25

cmResults <- cmResults %>% filter(analysisId == primaryAnalysisId, outcomeId == covidNarrowId)

table <- rbind(
  cmResults %>% filter(targetId == aceArbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "CCB/THZ (m)"),
  cmResults %>% filter(targetId == aceMonoId, comparatorId == arbMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "ARB (m)"),
  cmResults %>% filter(targetId == aceArbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "CCB/THZ (c)"),
  cmResults %>% filter(targetId == aceComboId, comparatorId == arbComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "ARB (c)")  
  ) %>% select(targetId, comparatorId, targetSubjects, comparatorSubjects, targetYears, comparatorYears, targetOutcomes, comparatorOutcomes, mdrr)

  table$targetSubjects <- formatC(table$targetSubjects, big.mark = ",", format = "d")
  table$comparatorSubjects <- formatC(table$comparatorSubjects, big.mark = ",", format = "d")
  table$targetYears <- formatC(table$targetYears, big.mark = ",", format = "d")
  table$comparatorYears <- formatC(table$comparatorYears, big.mark = ",", format = "d")
  table$targetOutcomes <- formatC(table$targetOutcomes, big.mark = ",", format = "d")
  table$comparatorOutcomes <- formatC(table$comparatorOutcomes, big.mark = ",", format = "d")
  # table$targetIr <- sprintf("%.2f", table$targetIr)
  # table$comparatorIr <- sprintf("%.2f", table$comparatorIr)
  table$mdrr <- sprintf("%.2f", table$mdrr)
  table$targetSubjects <- gsub("^-", "<", table$targetSubjects)
  table$comparatorSubjects <- gsub("^-", "<", table$comparatorSubjects)
  table$targetOutcomes <- gsub("^-", "<", table$targetOutcomes)
  table$comparatorOutcomes <- gsub("^-", "<", table$comparatorOutcomes)
  # table$targetIr <- gsub("^-", "<", table$targetIr)
  # table$comparatorIr <- gsub("^-", "<", table$comparatorIr)
```

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 diagnoses for ACEI, ARB and CCB/THZ monotherapy and in-combination user cohorts.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{rrrrrrrrr}
    \hiderowcolors
    \toprule
    &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
    \multicolumn{1}{c}{Target (T)} & \multicolumn{1}{c}{Comparator (C)} 
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(table, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}   


```{r, echo=FALSE}
source(system.file("shiny", "EvidenceExplorer", "PlotsAndTables.R",
                   package = "Covid19IncidenceRasInhibitors"))
source(system.file("shiny", "EvidenceExplorer", "DataPulls.R",
                   package = "Covid19IncidenceRasInhibitors"))
```

```{r, echo=FALSE, results="asis", cache=FALSE, warning=FALSE}


covariate <- readRDS(file.path(dataFolder, "covariate_SIDIAP.rds"))
colnames(covariate) <- SqlRender::snakeCaseToCamelCase(colnames(covariate))

balance <- getCovariateBalance(NULL, aceArbMonoId, ccbThzMonoId, databaseId = databaseId, analysisId = primaryAnalysisId, outcomeId = covidNarrowId)



#out <- lapply(balances_strat, function(tmp) {

  scale <- 0.55
  header <- readr::read_file("Table1Top.tex")
  # targetName <- (firstLineClasses %>% filter(cohortId == tmp$targetId))$shortName
  # comparatorName <- (firstLineClasses %>% filter(cohortId == tmp$comparatorId))$shortName

  # if (!(targetName == "THZ" && comparatorName == "ACEi")) {

  targetName <- "ACE/ARB monotherapy"
  comparatorName <- "CCB/THZ monotherapy"
  title <- sub(pattern = "Patient demographics",
               replacement = paste0("Baseline patient characteristcs for ", targetName," (T) and ", comparatorName, " (C) prevalent-users in the SIDIAP data source"),
               x = header)

  title <- sub("0.5\\\\textwidth", paste0(scale, "\\\\textwidth"), x = title)
  title <- sub("-0.5em", "+0.5em", x = title)

  title <- sub("% Extra row",
               paste0("& \\\\multicolumn{3}{c}{$N$ = XXX} & \\\\multicolumn{3}{c}{$N$ = XXX} \\\\\\\\"),
               # , "\\\\\\\\ \n",
               #        "\& \\\\multicolumn{3}{c}{Before stratification} \& \\\\multicolumn{3}{c}{After stratification} "),
               x = title)
  
  # if (targetName == "THZ" && comparatorName == "ARB") {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat*", title)
  # } else {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat", title)
  # }

  cat(title)

  # table <- prepareTable1(tmp$balance, pathToCsv = file.path("..", "Table1Specs.csv"))
  table <- prepareTable1(balance,pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv", 
                                      package = "Covid19IncidenceRasInhibitors"))
  table <- table[3:nrow(table),]

  print(xtable(table, format = "latex", align = c("l","l","r","r","r","r","r","r")),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE,
        add.to.row = list(pos = list(nrow(table)), command = c("\\bottomrule")),
        sanitize.text.function = identity)

  footer <- readr::read_file("Table1Botton.tex")
  cat(footer)
```


```{r}

  # }

  # plot <- plotCovariateBalanceScatterPlot(tmp$balance, labels = FALSE,
  #                                         beforeLabel = "Before stratification", afterLabel = "After stratification")
  #                                         # beforeLabel = "", afterLabel = "")
  #   suppressMessages(ggplot2::ggsave(paste0("scatter_", targetName, "_", comparatorName, ".pdf"), plot,
  #                                    width = 3, height = 3, units = "in"))
# })

# text <- prepareTable1(balance,
#               output = "latex",
#               pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv", 
#                                       package = "Covid19IncidenceRasInhibitors"))


# function(balance,
#                           beforeLabel = "Before stratification",
#                           afterLabel = "After stratification",
#                           targetLabel = "Target",
#                           comparatorLabel = "Comparator",
#                           percentDigits = 1,
#                           stdDiffDigits = 2,
#                           output = "latex",
#                           pathToCsv = "Table1Specs.csv") {

```

<!-- ```{r} -->
<!-- knitr::kable(tab, -->
<!--              format = "latex", escape = FALSE, longtable = TRUE, booktabs = TRUE, -->
<!--              caption = "\\textbf{Patient counts, total exposure and COVID-19 diagnoses}. We report study statistics (to change) for both monotherapy and in-combination cohort." -->
<!--              ) %>% -->
<!--   # kableExtra::column_spec(1, width="2cm") %>% -->
<!--   # kableExtra::column_spec(2, width="10cm") %>% -->
<!--   # kableExtra::column_spec(3, width="3cm") %>% -->
<!--   kableExtra::kable_styling(latex_options = "striped") -->
<!-- ``` -->

