---
params:
    save: NULL #"first.Rda"
    load: "first.Rda"
    completeReload: false
# bibliography: CohortDefinition.bib
# csl: nature-publishing-group-vancouver.csl
output:
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
    latex_engine: xelatex
mainfont: Arial
    #citation_package: natbib
    #rticles::sim_article
fontsize: 10pt
geometry: margin=1in
classoptions: doublespace
longtable: true
header-includes:
  - \usepackage[numbers,sort&compress]{natbib}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{caption}
  - \usepackage{rotating}
  - \usepackage{multirow}
  - \usepackage{mwe,tikz}
  - \usepackage[percent]{overpic}
  - \usepackage{enumitem}
  - \usepackage{mas_fun}
  - \usepackage{hyperref}
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
library(tidyr)
library(xtable)

readRdsCamelCase <- function(file) {
  result <- readRDS(file)
  colnames(result) <- SqlRender::snakeCaseToCamelCase(colnames(result))
  return(result)
}
```

\centerline{{\Huge Results: Incidence}}

<!-- \captionsetup[table]{name=Supplementary Table} -->
<!-- \captionsetup[figure]{name=Supplementary Figure} -->
\captionsetup{labelfont=bf}

# Cohorts

```{r, echo=FALSE}
cohorts <- read.csv(file = system.file("settings", "CohortsToCreate.csv", package = "Covid19IncidenceRasInhibitors")) %>% select(cohortId, shinyName)

aceMonoId <- cohorts %>% filter(shinyName == "ACE mono") %>% select(cohortId) %>% pull()
arbMonoId <- cohorts %>% filter(shinyName == "ARB mono") %>% select(cohortId) %>% pull()
aceArbMonoId <- cohorts %>% filter(shinyName == "ACE/ARB mono") %>% select(cohortId) %>% pull()
ccbThzMonoId <- cohorts %>% filter(shinyName == "CCB/THZ mono") %>% select(cohortId) %>% pull()

aceComboId <- cohorts %>% filter(shinyName == "ACE +combo") %>% select(cohortId) %>% pull()
arbComboId <- cohorts %>% filter(shinyName == "ARB +combo") %>% select(cohortId) %>% pull()
aceArbComboId <- cohorts %>% filter(shinyName == "ACE/ARB +combo") %>% select(cohortId) %>% pull()
ccbThzComboId <- cohorts %>% filter(shinyName == "CCB/THZ +combo") %>% select(cohortId) %>% pull()

ccbMonoId <- cohorts %>% filter(shinyName == "CCB mono") %>% select(cohortId) %>% pull()
thzMonoId <- cohorts %>% filter(shinyName == "THZ mono") %>% select(cohortId) %>% pull()
ccbComboId <- cohorts %>% filter(shinyName == "CCB +combo") %>% select(cohortId) %>% pull()
thzComboId <- cohorts %>% filter(shinyName == "THZ +combo") %>% select(cohortId) %>% pull()

covidNarrowId <- cohorts %>% filter(shinyName == "COVID-19 narrow") %>% select(cohortId) %>% pull()
covidBroadId <- cohorts %>% filter(shinyName == "COVID-19 broad") %>% select(cohortId) %>% pull()

pnaId <- cohorts %>% filter(shinyName == "Pneumonia") %>% select(cohortId) %>% pull()
adverseId <- cohorts %>% filter(shinyName == "Adverse event") %>% select(cohortId) %>% pull()

prettyNames <- data.frame(
  cohortId = c(aceMonoId, arbMonoId, aceArbMonoId, ccbMonoId, thzMonoId, ccbThzMonoId,
               aceComboId, arbComboId, aceArbComboId, ccbComboId, thzComboId, ccbThzComboId),
  cohortName = c("ACE", "ARB", "ACE/ARB", "CCB", "THZ", "CCB/THZ",
                 "ACE+", "ARB+", "ACE/ARB+", "CCB+", "THZ+", "CCB/THZ+"))

primaryAnalysisId <- 5 # Full stratified PS
```


# Sample sizes

```{r, echo=FALSE, warning=FALSE, message=FALSE}

sidiapDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/SIDIAP"
cuimcDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/CUIMC"
vaDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/VA-OMOP"
studyFolder <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors"

dataFolder <- file.path(sidiapDir, "shinyData")
databaseId <- "SIDIAP"

makeSampleSizeTable <- function(databaseId, 
                                dataFolder,
                                databaseOrder = 1) {
  cmResults <- readRDS(file = file.path(dataFolder, paste0("cohort_method_result_", databaseId, ".rds")))
  colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
  alpha <- 0.05
  power <- 0.8
  z1MinAlpha <- qnorm(1 - alpha/2)
  zBeta <- -qnorm(1 - power)
  pA <- cmResults$targetSubjects/(cmResults$targetSubjects + cmResults$comparatorSubjects)
  pB <- 1 - pA
  totalEvents <- abs(cmResults$targetOutcomes) + (cmResults$comparatorOutcomes)
  cmResults$mdrr <- exp(sqrt((zBeta + z1MinAlpha)^2/(totalEvents * pA * pB)))
  cmResults$targetYears <- cmResults$targetDays/365.25
  cmResults$comparatorYears <- cmResults$comparatorDays/365.25
  
  cmResults <- cmResults %>% filter(analysisId == primaryAnalysisId, outcomeId == covidNarrowId)
  
  table <- rbind(
    # cmResults %>% filter(targetId == aceArbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "CCB/THZ (m)"),
    # cmResults %>% filter(targetId == aceMonoId, comparatorId == arbMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "ARB (m)"),
    # cmResults %>% filter(targetId == aceArbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "CCB/THZ (c)"),
    # cmResults %>% filter(targetId == aceComboId, comparatorId == arbComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "ARB (c)")  
    cmResults %>% filter(targetId == aceArbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "CCB/THZ (m)", order = 1),
    cmResults %>% filter(targetId == aceArbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "CCB/THZ (c)", order = 2),
    cmResults %>% filter(targetId == aceMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "CCB/THZ (m)", order = 3),
    cmResults %>% filter(targetId == aceComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "CCB/THZ (c)", order = 4),
    cmResults %>% filter(targetId == arbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ARB (m)", comparatorId = "CCB/THZ (m)", order = 5),
    cmResults %>% filter(targetId == arbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ARB (c)", comparatorId = "CCB/THZ (c)", order = 6),
    cmResults %>% filter(targetId == aceMonoId, comparatorId == arbMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "ARB (m)", order = 7),
    cmResults %>% filter(targetId == aceComboId, comparatorId == arbComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "ARB (c)", order = 8) 
  ) %>% mutate (databaseId = databaseId, databaseOrder = databaseOrder) %>% 
    select(targetId, comparatorId, databaseId, targetSubjects, comparatorSubjects, targetYears, comparatorYears, targetOutcomes, comparatorOutcomes, mdrr, order, databaseOrder)
  
  table$targetSubjects <- formatC(table$targetSubjects, big.mark = ",", format = "d")
  table$comparatorSubjects <- formatC(table$comparatorSubjects, big.mark = ",", format = "d")
  table$targetYears <- formatC(table$targetYears, big.mark = ",", format = "d")
  table$comparatorYears <- formatC(table$comparatorYears, big.mark = ",", format = "d")
  table$targetOutcomes <- formatC(table$targetOutcomes, big.mark = ",", format = "d")
  table$comparatorOutcomes <- formatC(table$comparatorOutcomes, big.mark = ",", format = "d")
  # table$targetIr <- sprintf("%.2f", table$targetIr)
  # table$comparatorIr <- sprintf("%.2f", table$comparatorIr)
  table$mdrr <- sprintf("%.2f", table$mdrr)
  table$targetSubjects <- gsub("^-", "<", table$targetSubjects)
  table$comparatorSubjects <- gsub("^-", "<", table$comparatorSubjects)
  table$targetOutcomes <- gsub("^-", "<", table$targetOutcomes)
  table$comparatorOutcomes <- gsub("^-", "<", table$comparatorOutcomes)
  # table$targetIr <- gsub("^-", "<", table$targetIr)
  # table$comparatorIr <- gsub("^-", "<", table$comparatorIr)
  return(table)
}

tableSidiap <- makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), databaseOrder = 1)
tableVa <- makeSampleSizeTable(databaseId = "VA-OMOP", dataFolder = file.path(vaDir, "shinyData"), databaseOrder = 2)
tableCuimc <- makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), databaseOrder = 3)

table <- rbind(tableSidiap, tableCuimc, tableVa) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)
```

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 diagnoses for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(table, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0,1,2,3,4,5,6,7) * 3),
        command = c(
          "                       \\multicolumn{9}{l}{ACE/ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs ARB} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}   


```{r, echo=FALSE}
source(system.file("shiny", "EvidenceExplorer", "PlotsAndTables.R",
                   package = "Covid19IncidenceRasInhibitors"))
# source(system.file("shiny", "EvidenceExplorer", "DataPulls.R",
#                    package = "Covid19IncidenceRasInhibitors"))
```

```{r, echo=FALSE, results="asis", cache=FALSE, warning=FALSE}

getCovariateBalance <- function(connection,
                                targetId,
                                comparatorId,
                                databaseId,
                                analysisId,
                                covariate,
                                dataFolder,
                                outcomeId = NULL) {
  file <- sprintf("covariate_balance_t%s_c%s_%s.rds", targetId, comparatorId, databaseId)
  balance <- readRDS(file.path(dataFolder, file))
  colnames(balance) <- SqlRender::snakeCaseToCamelCase(colnames(balance))
  balance <- balance[balance$analysisId == analysisId & balance$outcomeId == outcomeId, ]
  balance <- merge(balance, covariate[covariate$databaseId == databaseId & covariate$analysisId == analysisId, 
                                      c("covariateId", "covariateAnalysisId", "covariateName")])
  balance <- balance[ c("covariateId",
                        "covariateName",
                        "covariateAnalysisId", 
                        "targetMeanBefore", 
                        "comparatorMeanBefore", 
                        "stdDiffBefore", 
                        "targetMeanAfter", 
                        "comparatorMeanAfter",
                        "stdDiffAfter")]
  colnames(balance) <- c("covariateId",
                         "covariateName",
                         "analysisId",
                         "beforeMatchingMeanTreated",
                         "beforeMatchingMeanComparator",
                         "beforeMatchingStdDiff",
                         "afterMatchingMeanTreated",
                         "afterMatchingMeanComparator",
                         "afterMatchingStdDiff")
  balance$absBeforeMatchingStdDiff <- abs(balance$beforeMatchingStdDiff)
  balance$absAfterMatchingStdDiff <- abs(balance$afterMatchingStdDiff)
  return(balance)
}


blend <- function(databaseIds,
                  targetId,
                  comparatorId,
                  dataFolders,
                  outcomeId = covidNarrowId) {

  covariate1 <- readRDS(file.path(dataFolders[1], paste0("covariate_", databaseIds[1], ".rds")))
  colnames(covariate1) <- SqlRender::snakeCaseToCamelCase(colnames(covariate1))

  balance1 <- getCovariateBalance(NULL, targetId, comparatorId, databaseId = databaseIds[1], analysisId = primaryAnalysisId,
                                  outcomeId = outcomeId,
                                  covariate = covariate1, dataFolder = dataFolders[1])

  covariate2 <- readRDS(file.path(dataFolders[2], paste0("covariate_", databaseIds[2], ".rds")))
  colnames(covariate2) <- SqlRender::snakeCaseToCamelCase(colnames(covariate2))

  balance2 <- getCovariateBalance(NULL, targetId, comparatorId, databaseId = databaseIds[2], analysisId = primaryAnalysisId,
                                  outcomeId = outcomeId,
                                  covariate = covariate2, dataFolder = dataFolders[2])
  
  covariate3 <- readRDS(file.path(dataFolders[3], paste0("covariate_", databaseIds[3], ".rds")))
  colnames(covariate3) <- SqlRender::snakeCaseToCamelCase(colnames(covariate3))

  balance3 <- getCovariateBalance(NULL, targetId, comparatorId, databaseId = databaseIds[3], analysisId = primaryAnalysisId,
                                  outcomeId = outcomeId,
                                  covariate = covariate3, dataFolder = dataFolders[3])
  
    specifications <- read.csv(system.file("shiny", "EvidenceExplorer", "Table1Specs.csv",
                                      package = "Covid19IncidenceRasInhibitors"), stringsAsFactors = FALSE)


  table1 <- prepareTable1(balance1,pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv",
                                      package = "Covid19IncidenceRasInhibitors"))

  table1 <- table1[3:nrow(table1),]
  colnames(table1) <- c("id","b","c","d","e","f","g")

  table2 <- prepareTable1(balance2,pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv",
                                      package = "Covid19IncidenceRasInhibitors"))

  table2 <- table2[3:nrow(table2),]
  colnames(table2) <- c("id","b","c","d","e","f","g")
  
  table3 <- prepareTable1(balance3,pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv",
                                      package = "Covid19IncidenceRasInhibitors"))

  table3 <- table3[3:nrow(table3),]
  colnames(table3) <- c("id","b","c","d","e","f","g")  
  
  harmonizeRace <- function(table) {
    
    aggregate <- function(x) {
      sprintf(" %1.2f", sum(as.numeric(x), na.rm = TRUE))
    }
    
    # Combine Asians
    combinedAsian <- c("    race = Asian", "    race = Asian Indian", "    race = Chinese", 
                       "    race = Filipino", "    race = Korean", "    race = Laotian", "    race = Vietnamese")
    asian <- table %>% filter(id %in% combinedAsian)
    b <- aggregate(asian$b)
    c <- aggregate(asian$c)
    e <- aggregate(asian$e)
    f <- aggregate(asian$f)
    
    asianKeep <- table$id == "    race = Asian"
    table$b[asianKeep] <- b
    table$c[asianKeep] <- c
    table$e[asianKeep] <- e
    table$f[asianKeep] <- f
    
    table <- table %>% filter(!(id %in% combinedAsian[-1]))
    
    # Recode Pacific Islander
    table$id <- as.character(table$id)
    table$id[table$id == "    race = Other Pacific Islander"] <- "    race = Native Hawaiian or Other Pacific Islander"
    return(table)
  }
  
  
  table1 <- harmonizeRace(table1)
  table2 <- harmonizeRace(table2)
  table3 <- harmonizeRace(table3)

  table1$order <- c(1:nrow(table1))
  table2$order <- c(1:nrow(table2))
  table3$order <- c(1:nrow(table3))

  return(list(table1, table2, table3, specifications,
              numCovariates = c(nrow(balance1), nrow(balance2), nrow(balance3))))
}

tmp <- blend(aceArbMonoId, ccbThzMonoId,
             databaseIds = c("SIDIAP", "VA-OMOP", "CUIMC"),
             dataFolders = c(dataFolder = file.path(sidiapDir, "shinyData"),
                             dataFolder = file.path(vaDir, "shinyData"),
                             dataFolder = file.path(cuimcDir, "shinyData")))
 
 numCovariates <- tmp$numCovariates
 names(numCovariates) <- c("SIDIAP", "VA-OMOP", "CUIMC")
 
 t2 <- full_join(tmp[[1]], tmp[[2]], by = "id")
 t2 <- full_join(t2, tmp[[3]], by = "id") %>% 
   rename(b.z = b, c.z = c, d.z = d, e.z = e, f.z = f, g.z = g, order.z = order)
 
tableOrder <- read.csv("CombinedDemographics.csv")

t3 <- full_join(t2, tableOrder, by = "id") %>% arrange(order) %>% 
  filter(order < 300) %>%
  mutate(id = newNames) %>%
  select(-order.x, -order.y, -order.z, -order, -newNames)
t3[is.na(t3)] <- ""
t3$id <- sub("    ", "\\\\hspace{1em} ", as.character(t3$id))

targetId <- aceArbMonoId
comparatorId <- ccbThzMonoId
databaseId = "SIDIAP, VA and CUIMC" 

# Get counts for header
sidiapTc <- tableSidiap %>% head(1) %>% select(targetSubjects, comparatorSubjects)
vaTc <- tableVa %>% head(1) %>% select(targetSubjects, comparatorSubjects)
cuimcTc <- tableCuimc %>% head(1) %>% select(targetSubjects, comparatorSubjects)

  scale <- 0.7
  header <- readr::read_file("Table1TopTriple.tex")

  targetName <- cohorts %>% filter(cohortId == targetId) %>% select(shinyName) %>% pull
  comparatorName <- cohorts %>% filter(cohortId == comparatorId) %>% select(shinyName) %>% pull
  title <- sub(pattern = "Patient demographics",
               replacement = paste0("Baseline patient characteristcs for ", targetName," (T) and ", comparatorName, " (C) prevalent-users in the ", databaseId, " data source"),
               x = header)

  title <- sub("0.5\\\\textwidth", paste0(scale, "\\\\textwidth"), x = title)
  title <- sub("-0.5em", "+0.5em", x = title)

  title <- gsub("% Extra row",
               paste0("& \\\\multicolumn{3}{c}{$N$ = ", sidiapTc$targetSubjects, 
                      " } & \\\\multicolumn{3}{c}{$N$ = ", sidiapTc$comparatorSubjects, " } ",
                      "& \\\\multicolumn{3}{c}{$N$ = ",     vaTc$targetSubjects, 
                      " } & \\\\multicolumn{3}{c}{$N$ = ",     vaTc$comparatorSubjects, " } ",
                      "& \\\\multicolumn{3}{c}{$N$ = ", cuimcTc$targetSubjects, 
                      " } & \\\\multicolumn{3}{c}{$N$ = ", cuimcTc$comparatorSubjects, " } ",
                      " \\\\\\\\"),
               # , "\\\\\\\\ \n",
               #        "\& \\\\multicolumn{3}{c}{Before stratification} \& \\\\multicolumn{3}{c}{After stratification} "),
               x = title)
  
  # if (targetName == "THZ" && comparatorName == "ARB") {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat*", title)
  # } else {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat", title)
  # }

  cat(title)
  
  table <- t3 # %>% select(-order.y, -order)

  print(xtable(table, format = "latex", align = c("l","l","r","r","r","r","r","r","r","r","r","r","r","r","r","r","r","r","r","r")),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE,
        add.to.row = list(pos = list(nrow(table)), command = c("\\bottomrule")),
        sanitize.text.function = identity)

  footer <- readr::read_file("Table1BottomTriple.tex")
  cat(footer)
#}

 # tmp <- makeCharacteristicsTable(aceArbMonoId, ccbThzMonoId, 
 #                          databaseIds = c("SIDIAP", "CUIMC"),
 #                          dataFolders = c(dataFolder = file.path(sidiapDir, "shinyData"),
 #                                          dataFolder = file.path(cuimcDir, "shinyData")))

# makeCharacteristicsTable(aceArbMonoId, ccbThzMonoId,   databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"))
# makeCharacteristicsTable(aceArbMonoId, ccbThzMonoId,   databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"))

```

## Numbers of covariates

```{r}
numCovariates
```

```{r, echo=FALSE, cache=TRUE}

tcs <- list(
  list(aceArbMonoId, ccbThzMonoId),
  list(aceArbComboId, ccbThzComboId),

  list(aceMonoId, ccbThzMonoId),
  list(aceComboId, ccbThzComboId),
  
  list(arbMonoId, ccbThzMonoId),
  list(arbComboId, ccbThzComboId),
  
  list(aceMonoId, arbMonoId),
  list(aceComboId, arbComboId)  
)
tcs <- lapply(tcs, function(x) { names(x) <- c("targetId", "comparatorId"); return(x) })

outcomesOfInterest <- c(123, 110, 139, 122) 

databaseId <- "SIDIAP"
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
cmResultsSidiap <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))

databaseId <- "VA-OMOP"
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
cmResultsVa <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))

databaseId <- "CUIMC"
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
cmResultsCuimc <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))

databaseId <- "Meta-analysis"
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
cmResultsMa <- cmResults %>% filter(outcomeId %in% outcomesOfInterest, analysisId %in% c(5,6))

cmResults <- rbind(cmResultsSidiap, cmResultsVa, cmResultsCuimc, cmResultsMa)

table <- do.call(
  "rbind",
  lapply(tcs, function(tc) {
    out <- cmResults %>% filter(targetId == tc$targetId, comparatorId == tc$comparatorId) %>%
      mutate(ci = sprintf("(%1.2f - %1.2f)", ci95Lb, ci95Ub),
             calibratedCi = sprintf("(%1.2f - %1.2f)", calibratedCi95Lb, calibratedCi95Ub)) %>%
      select(databaseId, targetId, comparatorId, outcomeId, analysisId,
             calibratedRr, calibratedCi, calibratedP, calibratedCi95Lb, calibratedCi95Ub, i2) %>%
      left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
      left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
      select(-targetId, -comparatorId) %>%
      select(targetName, comparatorName, everything())
    return(out)
  }))
```

```{r, echo=FALSE, cache=TRUE}
getCovariateBalance <- function(connection,
                                targetId,
                                comparatorId,
                                databaseId,
                                analysisId,
                                covariate,
                                dataFolder,
                                outcomeId = NULL) {
  file <- sprintf("covariate_balance_t%s_c%s_%s.rds", targetId, comparatorId, databaseId)
  balance <- readRDS(file.path(dataFolder, file))
  colnames(balance) <- SqlRender::snakeCaseToCamelCase(colnames(balance))
  balance <- balance[balance$analysisId == analysisId & balance$outcomeId == outcomeId, ]
  balance <- merge(balance, covariate[covariate$databaseId == databaseId & covariate$analysisId == analysisId, 
                                      c("covariateId", "covariateAnalysisId", "covariateName")])
  balance <- balance[ c("covariateId",
                        "covariateName",
                        "covariateAnalysisId", 
                        "targetMeanBefore", 
                        "comparatorMeanBefore", 
                        "stdDiffBefore", 
                        "targetMeanAfter", 
                        "comparatorMeanAfter",
                        "stdDiffAfter")]
  colnames(balance) <- c("covariateId",
                         "covariateName",
                         "analysisId",
                         "beforeMatchingMeanTreated",
                         "beforeMatchingMeanComparator",
                         "beforeMatchingStdDiff",
                         "afterMatchingMeanTreated",
                         "afterMatchingMeanComparator",
                         "afterMatchingStdDiff")
  balance$absBeforeMatchingStdDiff <- abs(balance$beforeMatchingStdDiff)
  balance$absAfterMatchingStdDiff <- abs(balance$afterMatchingStdDiff)
  return(balance)
}

sidiapCovariate <- readRdsCamelCase(file.path(sidiapDir, "shinyData", "covariate_SIDIAP.rds"))
cuimcCovariate <- readRdsCamelCase(file.path(cuimcDir, "shinyData", "covariate_CUIMC.rds"))
vaCovariate <- readRdsCamelCase(file.path(vaDir, "shinyData", "covariate_VA-OMOP.rds"))

getBalanceDiagnostic <- function(targetId, comparatorId, databaseId, analysisId, outcomeId, covariate, dataFolder) {
  balance <- getCovariateBalance(NULL, 
                                 targetId, comparatorId, 
                                 databaseId = databaseId, analysisId = analysisId, 
                                 outcomeId = outcomeId, 
                                 covariate = covariate, dataFolder = dataFolder)
  data.frame(databaseId = databaseId, analysisId = analysisId,
             targetId = targetId, comparatorId = comparatorId,
             imbalanced = sum(balance$absAfterMatchingStdDiff > 0.1))
}

balance<- 
  rbind(
    # SIDIAP 
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "SIDIAP", 5, covidNarrowId, sidiapCovariate,
                             file.path(sidiapDir, "shinyData"))
      })),
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "SIDIAP", 6, covidNarrowId, sidiapCovariate,
                             file.path(sidiapDir, "shinyData"))
      })),
    # VA
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "VA-OMOP", 5, covidNarrowId, vaCovariate,
                             file.path(vaDir, "shinyData"))
      })),
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "VA-OMOP", 6, covidNarrowId, vaCovariate,
                             file.path(vaDir, "shinyData"))
      })),    
    # CUIMC
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "CUIMC", 5, covidNarrowId, cuimcCovariate,
                             file.path(cuimcDir, "shinyData"))
      })),
    do.call(
      "rbind",
      lapply(tcs, function(tc) {
        getBalanceDiagnostic(tc$targetId, tc$comparatorId, "CUIMC", 6, covidNarrowId, cuimcCovariate,
                             file.path(cuimcDir, "shinyData"))
      }))    
  ) %>% 
  left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
  left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
  select(-targetId, -comparatorId) %>%
  select(targetName, comparatorName, everything())  

  # Add meta-analysis
  meta <- balance %>% filter(databaseId == "SIDIAP") %>% mutate(databaseId = "Meta-analysis",
                                                                imbalanced = 0)
  balance <- rbind(balance, meta) # Comment out to remove meta-analysis

table <- inner_join(table, balance, by = c("targetName", "comparatorName", "databaseId", "analysisId"))

knitr::kable(table %>% filter(outcomeId == covidNarrowId, databaseId == "Meta-analysis") %>%
               arrange(analysisId) %>%
               filter(!is.na(is)) %>% select(targetName, comparatorName, analysisId, databaseId, i2), 
             format = "latex",
             booktabs = TRUE)

table <- table %>% select(-i2)

```


```{r, echo=FALSE}
table5 <- table %>% filter(analysisId == 5) %>% select(-analysisId) %>%
  select(-calibratedCi95Lb, -calibratedCi95Ub) %>%
  rename(stratCalRr = calibratedRr, stratCalCi = calibratedCi, stratCalP = calibratedP, stratImbalanced = imbalanced)
table6 <- table %>% filter(analysisId == 6) %>% select(-analysisId) %>%
  select(-calibratedCi95Lb, -calibratedCi95Ub) %>%
  rename(matchCalRr = calibratedRr, matchCalCi = calibratedCi, matchCalP = calibratedP, matchImbalanced = imbalanced)
wideTable <- inner_join(table5, table6, by = c("databaseId", "targetName", "comparatorName", "outcomeId"))
```

\begin{table}[H]
 \caption{Relative risk of COVID-19 diagnosis for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrr}
    \hiderowcolors
    \toprule
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}

numDb <- length(unique(wideTable$databaseId))

print(xtable(wideTable %>% filter(outcomeId == covidNarrowId) %>% 
               select(-outcomeId, -stratImbalanced, -matchCalRr, -matchCalCi, -matchCalP, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0:7) * numDb),
        command = c(
          "                       \\multicolumn{6}{l}{ACE/ARB vs CCB/THZ} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{5}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{6}{l}{ACE vs ARB} \\\\ & \\multicolumn{5}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{5}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\definecolor{light-gray}{gray}{0.50}
\begin{table}[H]
 \caption{Relative risk of COVID-19 diagnosis for ACE inhibitors, ARB, CCB and THZ prevalent-users. We report calibrated hazard ratios (HRs) and their 95\% confidence intervals (CIs) across data sources. Grayed out entries do not pass study diagnostics.}
  \rowcolors{2}{gray!6}{white}
  \centering{
  \begin{tabular}{p{-2em}p{-2em}lrrrrrr}
    \hiderowcolors
    \toprule
    & & & \multicolumn{3}{c}{PS-stratified} & \multicolumn{3}{c}{PS-matched} \\
     \cmidrule(lr){4-6} \cmidrule(lr){7-9}
     & 
    & & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$}
      & \multicolumn{1}{c}{HR} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$p$} \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}

# Annotate

toString <- function(x) {
  ifelse(sapply(x, is.numeric),
         sprintf("%1.2f", x),
         x)
}

stratAnnotate <- function(x) {
  str <- toString(x)
  ifelse(wideTable$stratImbalanced > 0,
         paste0("{\\color{light-gray}", str, "}"),
         str)
}

matchAnnotate <- function(x) {
  str <- toString(x)
  ifelse(wideTable$matchImbalanced > 0,
         paste0("{\\color{light-gray}", str, "}"),
         str)
}

annotatedWideTable <- wideTable %>% 
  mutate(stratCalRr = stratAnnotate(stratCalRr),
         stratCalCi = stratAnnotate(stratCalCi),
         stratCalP = stratAnnotate(stratCalP)) %>%
  mutate(matchCalRr = matchAnnotate(matchCalRr),
         matchCalCi = matchAnnotate(matchCalCi),
         matchCalP = matchAnnotate(matchCalP))

print(xtable(annotatedWideTable %>% filter(outcomeId == covidNarrowId) %>% 
               select(-outcomeId, -stratImbalanced, -matchImbalanced) %>%
               mutate(targetName = "", comparatorName = ""), 
             format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
 add.to.row = list(
        pos = as.list(c(0:7) * numDb),
        command = c(
          "                       \\multicolumn{9}{l}{ACE/ARB vs CCB/THZ} \\\\ & \\multicolumn{8}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs CCB/THZ} \\\\ & \\multicolumn{8}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ARB vs CCB/THZ} \\\\ & \\multicolumn{8}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{ACE vs ARB} \\\\ & \\multicolumn{8}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"          
          )
      ),      
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}

\clearpage

```{r, echo=FALSE, warning=FALSE}

design <- data.frame(
  databaseId = c("SIDIAP", "VA-OMOP", "CUIMC", "Meta-analysis"),
  point = c(20, 20, 18, 20)
)

poorBalance <- "grey70"

table5 <- table %>% 
  left_join(design, by = "databaseId") %>% 
  filter(analysisId == 5) %>% 
  mutate(point = 21, size = 0.6) %>%
  mutate(color = ifelse(imbalanced > 0, poorBalance, "black")) %>%
  mutate(balanceColor = ifelse(imbalanced > 0, poorBalance, "black"))
table6 <- table %>% 
  left_join(design, by = "databaseId") %>% 
  filter(analysisId == 6) %>% 
  mutate(point = 21,size = 0.6) %>%
  mutate(color = ifelse(imbalanced > 0, "white", "white")) %>%
  mutate(balanceColor = ifelse(imbalanced > 0, poorBalance, "black"))

delta5 <- 0
delta6 <- 0

do56 <- TRUE
if (do56) {
  delta5 <- +0.25
  delta6 <- -0.25
}

pdf(file = "SixEffect.pdf", height = 8, width = 6)

dbs <- numDb

map <- function(index) {
  floor(index / dbs) + 2 * floor(index / (2 * dbs)) + 3 + index
}

tab <- table5 %>% filter(outcomeId == covidNarrowId) %>%
  mutate(index = row_number() - 1,
         row = map(index))

ymax <- max(tab$row)

par(mar = c(1,1,1,1))

plot(0,0, type = "n",
     ylim = c(-3, ymax),
     xlim = c(0, 12), axes = FALSE, 
     ylab = "", xlab = "")

textCex <- 0.6

cohortNames <- c("ACE/ARB vs CCB/THZ", "ACE vs CCB/THZ", "ARB vs CCB/THZ", "ACE vs ARB")
cohortPositions <- (c(1:length(cohortNames)) - 1) * (2 * dbs + 4) + 1
text(x = 0, y = ymax - cohortPositions, labels = cohortNames, pos = 4, cex = textCex)

minorNames <- rep(c("Monotherapy", "+ Combination"), length(cohortNames))
minorTicks <- tab %>% filter(databaseId == "SIDIAP") %>% select(row) %>% pull() - 1
text(x = 0.25, y = ymax - minorTicks, labels = minorNames, pos = 4, cex = textCex)

text(x = 0.5, y = ymax - tab$row, labels = tab$databaseId, pos = 4, cex = textCex)

start <- 3.5
width <- 2
spacer <- 2.4
tick <- 0.1

scaleMin <- 1/4  # -1
scaleMax <- 4    # +1

points(x = 4, y = ymax - 0.5, pch = 21, bg = "black")
text(x = 4.025, y = ymax - 0.5, labels = "PS-stratified", 
     pos = 4, cex = textCex, adj = 0.5)

points(x = 6, y = ymax - 0.5, pch = 21, bg = "white")
text(x = 6.025, y = ymax - 0.5, labels = "PS-matched", 
     pos = 4, cex = textCex, adj = 0.5)

points(x = 8, y = ymax - 0.5, pch = 22, bg = poorBalance, col = poorBalance)
text(x = 8.025, y = ymax - 0.5, labels = "fails study diagnostics", 
     pos = 4, cex = textCex, adj = 0.5)

scale <- function(x) {
  log(x) / (log(scaleMax) - log(scaleMin)) * width
}

clip_min <- function(x) {
  pmax(x, -width / 2)
}

clip_max <- function(x) {
  pmin(x, +width / 2)
}

clip_rm <- function(x) {
  x[x > width / 2] <- NA
  x[x < -width / 2] <- NA
  x
}

library(wesanderson)

outcomeIds <- c(covidNarrowId, covidBroadId, pnaId, adverseId)
outcomeNames <- c("Diagnosis", "+Hospital", "PNA", "PAAS")
outcomeColors <- c(wes_palette("Moonrise3")[5],
                   wes_palette("Moonrise2")[2],
                   wes_palette("Moonrise2")[3],
                   wes_palette("Moonrise3")[3])

designColors <- c(wes_palette("Moonrise2")[1],
                   wes_palette("Moonrise2")[2])
balancePointColor <- wes_palette("Moonrise2")[4]

outcomeColors <- adjustcolor(outcomeColors, alpha.f = 0.2)
designColors <- adjustcolor(designColors, alpha.f = 0.2)

for (i in 1:4) {

  offset <- start + (i - 1) * spacer

  rect(xleft = offset + scale(scaleMin),
       xright = offset + scale(scaleMax),
       ytop = ymax - 2,
       ybottom = -0.5,
       col = outcomeColors[i], #"grey90",
       border = NA)

  segments(x0 = offset, x1 = offset,
           y0 = -0.5, y1 = ymax - 2, lty = 3)

  # Stratification

  tab <- table5 %>% filter(outcomeId == outcomeIds[i]) %>%
    mutate(index = row_number() - 1,
           row = map(index))

  segments(x0 = offset + clip_min(scale(tab$calibratedCi95Lb)),
           x1 = offset + clip_max(scale(tab$calibratedCi95Ub)),
           y0 = ymax - tab$row + delta5, y1 = ymax - tab$row + delta5,
           col = tab$balanceColor)

  segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
           x1 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
           y0 = ymax - tab$row + tick + delta5,
           y1 = ymax - tab$row - tick + delta5,
           col = tab$balanceColor)

  segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
           x1 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
           y0 = ymax - tab$row + tick + delta5,
           y1 = ymax - tab$row - tick + delta5,
           col = tab$balanceColor)

  points(x = offset + clip_rm(scale(tab$calibratedRr)),
         y = ymax - tab$row + delta5,
         pch = tab$point,
         bg = tab$color,
         cex = tab$size,
         col = tab$balanceColor)

  if (do56) {

    # Matching
    tab <- table6 %>% filter(outcomeId == outcomeIds[i]) %>%
      mutate(index = row_number() - 1,
             row = map(index))

    segments(x0 = offset + clip_min(scale(tab$calibratedCi95Lb)),
             x1 = offset + clip_max(scale(tab$calibratedCi95Ub)),
             y0 = ymax - tab$row + delta6, y1 = ymax - tab$row + delta6,
             col = tab$balanceColor)

    segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
             x1 = offset + clip_rm(scale(tab$calibratedCi95Lb)),
             y0 = ymax - tab$row + tick + delta6,
             y1 = ymax - tab$row - tick + delta6,
             col = tab$balanceColor)

    segments(x0 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
             x1 = offset + clip_rm(scale(tab$calibratedCi95Ub)),
             y0 = ymax - tab$row + tick + delta6,
             y1 = ymax - tab$row - tick + delta6,
             col = tab$balanceColor)

    points(x = offset + clip_rm(scale(tab$calibratedRr)),
           y = ymax - tab$row + delta6,
           pch = tab$point,
           bg = tab$color,
           cex = tab$size,
           col = tab$balanceColor)
  }

  # Bottom marks

  bt <- -0.75

  segments(x0 = offset - width / 2,
           x1 = offset + width / 2,
           y0 = bt, y1 = bt)

  marks <- scale(c(1/4, 1/2, 1, 2, 4))
  labels <- c("1/4", "1/2", "1", "2", "4")

  segments(x0 = offset + marks,
           x1 = offset + marks,
           y0 = bt,
           y1 = bt - 0.2)

  text(x = offset + marks,
       y = bt - 0.1,
       labels = labels,
       pos = 1, cex = textCex)

  text(x = offset,
       y = bt - 2,
       labels = outcomeNames[i],
       cex = 0.8)
}

invisible(dev.off())

```


\begin{figure}[H]
  \caption{Relative risk of COVID-19-related outcomes for ACE inhibitor, ARB, CCB and THZ prevalent-users.  
    Outcomes are COVID-19 diagnosis, COVID-19 hospitalization (+Hospital), patients hospitalized with pneumonia (PNA) and patients hospitalized with pneunomia, acute respiratory distree syndrome, acute kidney injury or sepsis (PAAS). 
    We plot calibrated hazard ratios (circles) and their 95% confidence intervals (wiskers) for both monotherapy and in-combination cohort definitions,
    labeled by propensity score (PS) adjustment method (black/white), across data sources.  Grayed out entries do not pass study diagnostics.}
  \centerline{
    \includegraphics[width=0.95\textwidth]{SixEffect}
  }
\end{figure}

# Min/max covariate counts across data sources

```{r, echo=FALSE, cache=TRUE}
# SIDIAP
files <- list.files(file.path(sidiapDir, "shinyData"),
                    pattern = "covariate_balance_t\\d",
                    full.names = TRUE)

sidiapCounts <- do.call("rbind.data.frame",
                        lapply(files, function(file) {
                          bal <- readRDS(file)
                          t <- sub(".*t", "", file)
                          target <- sub("_.*", "", t)
                          c <- sub(".*c", "", file)
                          comparator <- sub("_.*", "", c)
                          return(list(rows = bal %>% filter(analysis_id == primaryAnalysisId,
                                                            outcome_id == covidNarrowId) %>% nrow(),
                                      target = as.numeric(target),
                                      comparator = as.numeric(comparator)))
                        }))

# VA
files <- list.files(file.path(vaDir, "shinyData"),
                    pattern = "covariate_balance_t\\d",
                    full.names = TRUE)

vaCounts <- do.call("rbind.data.frame",
                        lapply(files, function(file) {
                          bal <- readRDS(file)
                          t <- sub(".*t", "", file)
                          target <- sub("_.*", "", t)
                          c <- sub(".*c", "", file)
                          comparator <- sub("_.*", "", c)
                          return(list(rows = bal %>% filter(analysis_id == primaryAnalysisId,
                                                            outcome_id == covidNarrowId) %>% nrow(),
                                      target = as.numeric(target),
                                      comparator = as.numeric(comparator)))
                        }))


#CUIMC
files <- list.files(file.path(cuimcDir, "shinyData"),
                    pattern = "covariate_balance_t\\d",
                    full.names = TRUE)

cuimcCounts <- do.call("rbind.data.frame",
                       lapply(files, function(file) {
                         bal <- readRDS(file)
                         t <- sub(".*t", "", file)
                         target <- sub("_.*", "", t)
                         c <- sub(".*c", "", file)
                         comparator <- sub("_.*", "", c)
                         return(list(rows = bal %>% filter(analysis_id == primaryAnalysisId,
                                                            outcome_id == covidNarrowId) %>% nrow(),
                                     target = as.numeric(target),
                                     comparator = as.numeric(comparator)))
                       }))
```

```{r, echo=FALSE}
#library(dplyr)
sidiapCounts %>% filter(rows == max(sidiapCounts$rows) | rows == min(sidiapCounts$rows)) %>%
  inner_join(cohorts, by = c("target" = "cohortId")) %>%
  rename(targetName = shinyName) %>%
  inner_join(cohorts, by = c("comparator" = "cohortId")) %>%
  rename(comparatorName = shinyName) %>%
  select(rows, targetName, comparatorName) %>% mutate(databaseId = "SIDIAP")

vaCounts %>% filter(rows == max(vaCounts$rows) | rows == min(vaCounts$rows)) %>%
  inner_join(cohorts, by = c("target" = "cohortId")) %>%
  rename(targetName = shinyName) %>%
  inner_join(cohorts, by = c("comparator" = "cohortId")) %>%
  rename(comparatorName = shinyName) %>%
  select(rows, targetName, comparatorName) %>% mutate(databaseId = "VA-OMOP")

cuimcCounts %>% filter(rows == max(cuimcCounts$rows) | rows == min(cuimcCounts$rows)) %>%
  inner_join(cohorts, by = c("target" = "cohortId")) %>%
  rename(targetName = shinyName) %>%
  inner_join(cohorts, by = c("comparator" = "cohortId")) %>%
  rename(comparatorName = shinyName) %>%
  select(rows, targetName, comparatorName) %>% mutate(databaseId = "CUIMC")
```

# Important PS variables
```{r, echo=FALSE, cache=TRUE}
files <- list.files(file.path(sidiapDir, "shinyData"),
                    pattern = "covariate_balance_t\\d",
                    full.names = TRUE)

getTopPsCovariates <- function(studyFolder, databaseId, length = 25) {
  psModel <- readRdsCamelCase(file.path(studyFolder, "shinyData", paste0("propensity_model_", databaseId, ".rds")))
  covariate <- readRdsCamelCase(file.path(studyFolder, "shinyData", paste0("covariate_", databaseId, ".rds")))
  psModel <- psModel %>%
    left_join(covariate, by = c("databaseId", "analysisId", "covariateId")) %>% filter(analysisId == 5)
  psFreq <- psModel %>% count(covariateId, covariateName) %>% arrange(-n) %>% head(length)

  return(psFreq)
}
```

## SIDIAP

```{r, echo=FALSE}
sidiapFreq <- getTopPsCovariates(sidiapDir, "SIDIAP", length = 40)
knitr::kable(sidiapFreq, longtable = TRUE) %>% kableExtra::column_spec(2, width = "40em")
```

## VA

```{r, echo=FALSE}
vaFreq <- getTopPsCovariates(vaDir, "VA-OMOP", length = 40)
knitr::kable(vaFreq, longtable = TRUE) %>% kableExtra::column_spec(2, width = "40em")
```

## CUIMC

```{r, echo=FALSE}
cuimcFreq <- getTopPsCovariates(cuimcDir, "CUIMC", length = 40)
knitr::kable(cuimcFreq, longtable = TRUE) %>% kableExtra::column_spec(2, width = "40em")
```

# Balance plots

```{r, echo=FALSE, warning=FALSE, message=FALSE}

plotCovariateBalanceScatterPlot <- function(balance, 
                                            beforeLabel = "Before stratification", 
                                            afterLabel = "After stratification",
                                            limits, yLimits,
                                            backgroundColor = "lightgrey",
                                            pointColor = rgb(0, 0, 0.8)) {
  
  if (missing(limits) || is.na(limits)) {
    limits <- c(min(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                    na.rm = TRUE),
                max(c(balance$absBeforeMatchingStdDiff, balance$absAfterMatchingStdDiff),
                    na.rm = TRUE))
  }
  
  if (missing(yLimits) || is.na(yLimits)) {
    yLimits <- limits
  }
  theme <- ggplot2::element_text(colour = "#000000", size = 12)
  plot <- ggplot2::ggplot(balance, ggplot2::aes(x = absBeforeMatchingStdDiff, y = absAfterMatchingStdDiff)) +
    ggplot2::geom_point(color = adjustcolor(pointColor, alpha.f = 0.3), 
                        shape = 16, size = 2) +
    ggplot2::geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ggplot2::geom_hline(yintercept = 0) +
    ggplot2::geom_vline(xintercept = 0) +
    ggplot2::scale_x_continuous(beforeLabel, limits = limits) +
    ggplot2::scale_y_continuous(afterLabel, limits = yLimits) +
    ggplot2::theme(text = theme,
                   axis.text.x = ggplot2::element_text(colour="black"),
                   axis.text.y = ggplot2::element_text(colour="black"),
                   panel.background = ggplot2::element_rect(fill = backgroundColor,
                                                            colour = backgroundColor,
                                                            size = 0.5, linetype = "solid"))
  return(plot)
}
```

## Across data sources

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}

library(cowplot)

getAllBalancePlots <- function(targetId, comparatorId, limits, yLimits) {

  balanceStrat <- list(
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 5, outcomeId = covidNarrowId,
                          databaseId = "SIDIAP", covariate = sidiapCovariate,
                          dataFolder = file.path(studyFolder, "SIDIAP", "shinyData")),
      beforeLabel = "Before stratification", afterLabel = "After stratification", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[1], pointColor = balancePointColor),
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 5, outcomeId = covidNarrowId,
                          databaseId = "VA-OMOP", covariate = vaCovariate,
                          dataFolder = file.path(studyFolder, "VA-OMOP", "shinyData")),
      beforeLabel = "Before stratification", afterLabel = "After stratification", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[1], pointColor = balancePointColor), 
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 5, outcomeId = covidNarrowId,
                          databaseId = "CUIMC", covariate = cuimcCovariate,
                          dataFolder = file.path(studyFolder, "CUIMC", "shinyData")),
      beforeLabel = "Before stratification", afterLabel = "After stratification", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[1], pointColor = balancePointColor))
  balanceMatch <- list(
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 6, outcomeId = covidNarrowId,
                          databaseId = "SIDIAP", covariate = sidiapCovariate,
                          dataFolder = file.path(studyFolder, "SIDIAP", "shinyData")),
      beforeLabel = "Before matching", afterLabel = "After matching", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[2], pointColor = balancePointColor),
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 6, outcomeId = covidNarrowId,
                          databaseId = "VA-OMOP", covariate = vaCovariate,
                          dataFolder = file.path(studyFolder, "VA-OMOP", "shinyData")),
      beforeLabel = "Before matching", afterLabel = "After matching", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[2], pointColor = balancePointColor), 
    plotCovariateBalanceScatterPlot(
      getCovariateBalance(NULL, targetId, comparatorId, analysisId = 6, outcomeId = covidNarrowId,
                          databaseId = "CUIMC", covariate = cuimcCovariate,
                          dataFolder = file.path(studyFolder, "CUIMC", "shinyData")),
      beforeLabel = "Before matching", afterLabel = "After matching", 
      limits = limits, yLimits = yLimits, backgroundColor = designColors[2], pointColor = balancePointColor))    
  return(list(strat = balanceStrat, match = balanceMatch))
}

saveAllBalancePlots <- function(balance, file) {
  
  sidiap <-  ggplot2::ggplot() + 
    ggplot2::annotate("text", x = 0, y = 0, size = 6, angle = -90, label = "SIDIAP      ") + ggplot2::theme_void()

  va <-  ggplot2::ggplot() + 
    ggplot2::annotate("text", x = 0, y = 10, size = 6, angle = -90, label = "VA-OMOP      ") + ggplot2::theme_void()
  
  cuimc <-  ggplot2::ggplot() + 
    ggplot2::annotate("text", x = 0, y = 0, size = 6, angle = -90, label = "CUIMC      ") + ggplot2::theme_void()  
  
  invisible(save_plot(file,
                      plot_grid(
                        balance$strat[[1]], balance$match[[1]], sidiap,
                        balance$strat[[2]], balance$match[[2]], va,
                        balance$strat[[3]], balance$match[[3]], cuimc,
                        ncol = 3, rel_widths = c(1, 1, 0.1))
                      ,
                      base_asp = 3 * 2/3, 
                      #ncol = 5,
                      base_height = 6))
}

saveAllBalancePlots(getAllBalancePlots(aceArbMonoId, ccbThzMonoId, limits = c(0, 0.6), yLimits = c(0, 0.2)),
                    file = "allBalanceRasMono.pdf")

saveAllBalancePlots(getAllBalancePlots(arbComboId, ccbThzComboId, limits = c(0, 0.45), yLimits = c(0, 0.35)),
                    file = "allBalanceArbCombo.pdf")

saveAllBalancePlots(getAllBalancePlots(aceComboId, arbComboId, limits = c(0, 0.45), yLimits = c(0, 0.35)),
                    file = "allBalanceAceArbCombo.pdf")
```


\begin{figure}[H]
  \caption{Covariate balance between ACE/ARB mono and CCB/THZ mono prevalent-user cohorts.  We plot balance before and after stratification and matching across data sources.}
  \centering{
    \includegraphics[width=0.9\textwidth]{allBalanceRasMono}
  }
\end{figure}

\begin{figure}[H]
  \caption{Covariate balance between ARB combo and CCB/THZ mono prevalent-user cohorts.  We plot balance before and after stratification and matching across data sources.}
  \centering{
    \includegraphics[width=0.9\textwidth]{allBalanceArbCombo}
  }
\end{figure}

\begin{figure}[H]
  \caption{Covariate balance between ACE combo and ARB combo prevalent-user cohorts.  We plot balance before and after stratification and matching across data sources.}
  \centering{
    \includegraphics[width=0.9\textwidth]{allBalanceAceArbCombo.pdf}
  }
\end{figure}

## Just CUIMC case

```{r, echo=FALSE, warning=FALSE, message=FALSE}
covariate <- readRDS(file.path(studyFolder, "CUIMC", "shinyData", paste0("covariate_", "CUIMC", ".rds")))
colnames(covariate) <- SqlRender::snakeCaseToCamelCase(colnames(covariate))

balanceStrat <- getCovariateBalance(NULL, arbComboId, ccbThzComboId, databaseId = "CUIMC", analysisId = primaryAnalysisId,
                                    outcomeId = covidNarrowId,
                                    covariate = covariate,
                                    dataFolder = file.path(studyFolder, "CUIMC", "shinyData"))

plotStrat <- plotCovariateBalanceScatterPlot(balanceStrat,
                                             beforeLabel = "Before stratification",
                                             afterLabel = "After stratification")

balanceMatch <- getCovariateBalance(NULL, arbComboId, ccbThzComboId, databaseId = "CUIMC", analysisId = 6,
                                    outcomeId = covidNarrowId,
                                    covariate = covariate,
                                    dataFolder = file.path(studyFolder, "CUIMC", "shinyData"))

plotMatch <- plotCovariateBalanceScatterPlot(balanceMatch,
                                             beforeLabel = "Before matching",
                                             afterLabel = "After matching")

library(ggplot2)
ggsave("plotStratArb.pdf", plot = plotStrat, width = 4, height = 4)
ggsave("plotMatchArb.pdf", plot = plotMatch, width = 4, height = 4)

balanceStratArb <- balanceStrat

balanceStrat <- getCovariateBalance(NULL, aceComboId, arbComboId, databaseId = "CUIMC", analysisId = primaryAnalysisId,
                                    outcomeId = covidNarrowId,
                                    covariate = covariate,
                                    dataFolder = file.path(studyFolder, "CUIMC", "shinyData"))

plotStrat <- plotCovariateBalanceScatterPlot(balanceStrat,
                                             beforeLabel = "Before stratification",
                                             afterLabel = "After stratification")

balanceMatch <- getCovariateBalance(NULL, aceComboId, arbComboId, databaseId = "CUIMC", analysisId = 6,
                                    outcomeId = covidNarrowId,
                                    covariate = covariate,
                                    dataFolder = file.path(studyFolder, "CUIMC", "shinyData"))

plotMatch <- plotCovariateBalanceScatterPlot(balanceMatch,
                                             beforeLabel = "Before matching",
                                             afterLabel = "After matching")

balanceStratAce <- balanceStrat

library(ggplot2)
ggsave("plotStratAce.pdf", plot = plotStrat, width = 4, height = 4)
ggsave("plotMatchAce.pdf", plot = plotMatch, width = 4, height = 4)

```

\begin{figure}[H]
  \caption{ARB combo vs CCB/THZ combo in CUIMC.}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{plotStratArb} \includegraphics[width=0.4\textwidth]{plotMatchArb}
  \end{center}
\end{figure}

\begin{figure}[H]
  \caption{ACE combo vs ARB combo in CUIMC.}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{plotStratAce} \includegraphics[width=0.4\textwidth]{plotMatchAce}
  \end{center}
\end{figure}

## Info about ARB vs CCB/THZ the extreme values in CUIMC stratification:
```{r}
maxIndex <- which(balanceStratArb$absBeforeMatchingStdDiff == max(
  balanceStratArb$absBeforeMatchingStdDiff))
balanceStratArb[maxIndex,
                c("covariateName", "beforeMatchingMeanTreated", 
                  "beforeMatchingMeanComparator")]

```

## Info about ACE vs ARB the extreme values in CUIMC stratification:
```{r}
maxIndex <- which(balanceStratAce$absBeforeMatchingStdDiff > 0.3)
balanceStratAce[maxIndex,
                c("covariateName", "beforeMatchingMeanTreated", 
                  "beforeMatchingMeanComparator")]

```


