---
params:
    save: NULL #"first.Rda"
    load: "first.Rda"
    completeReload: false
# bibliography: CohortDefinition.bib
# csl: nature-publishing-group-vancouver.csl
output:
  pdf_document:
    keep_tex: true
    md_extensions: +raw_attribute
    latex_engine: xelatex
mainfont: Arial    
fontsize: 11pt
geometry: margin=1in
classoptions: doublespace
longtable: true
header-includes:
  - \usepackage[numbers,sort&compress]{natbib}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{caption}
  - \usepackage{rotating}
  - \usepackage{multirow}
  - \usepackage{mwe,tikz}
  - \usepackage[percent]{overpic}
  - \usepackage{enumitem}
  - \usepackage{mas_fun}
  - \usepackage{hyperref}
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage[table]{xcolor}', x, fixed = TRUE)})
library(dplyr)
library(tidyr)
library(xtable)
```

\centerline{{\Huge Supplementary Material: Incidence}}
\vspace{1.0em}
\centerline{\Large for}
\vspace{1.0em}
\centerline{\huge Comprehensive comparative effectiveness and safety of}
\centerline{\huge first-line antihypertensive drug classes}
\vspace{1.0em}
\centerline{\Large by}
\vspace{1.0em}
\centerline{\Large Marc A. Suchard, Martijn J. Schuemie, Harlan Krumholz,}
\centerline{\Large Seng Chan You, RuiJen Chen, Nicole Pratt, Christian G. Reich,}
\centerline{\Large Jon Duke, David Madigan, George Hripcsak and Patrick B.Ryan}

\tableofcontents

\captionsetup[table]{name=Supplementary Table}
\captionsetup[figure]{name=Supplementary Figure}
\captionsetup{labelfont=bf}

\renewcommand\theContinuedFloat{\alph{ContinuedFloat}}

```{r, echo=FALSE}
cohorts <- read.csv(file = system.file("settings", "CohortsToCreate.csv", package = "Covid19IncidenceRasInhibitors")) %>% select(cohortId, shinyName)

aceMonoId <- cohorts %>% filter(shinyName == "ACE mono") %>% select(cohortId) %>% pull()
arbMonoId <- cohorts %>% filter(shinyName == "ARB mono") %>% select(cohortId) %>% pull()
aceArbMonoId <- cohorts %>% filter(shinyName == "ACE/ARB mono") %>% select(cohortId) %>% pull()
ccbThzMonoId <- cohorts %>% filter(shinyName == "CCB/THZ mono") %>% select(cohortId) %>% pull()

aceComboId <- cohorts %>% filter(shinyName == "ACE +combo") %>% select(cohortId) %>% pull()
arbComboId <- cohorts %>% filter(shinyName == "ARB +combo") %>% select(cohortId) %>% pull()
aceArbComboId <- cohorts %>% filter(shinyName == "ACE/ARB +combo") %>% select(cohortId) %>% pull()
ccbThzComboId <- cohorts %>% filter(shinyName == "CCB/THZ +combo") %>% select(cohortId) %>% pull()

ccbMonoId <- cohorts %>% filter(shinyName == "CCB mono") %>% select(cohortId) %>% pull()
thzMonoId <- cohorts %>% filter(shinyName == "THZ mono") %>% select(cohortId) %>% pull()
ccbComboId <- cohorts %>% filter(shinyName == "CCB +combo") %>% select(cohortId) %>% pull()
thzComboId <- cohorts %>% filter(shinyName == "THZ +combo") %>% select(cohortId) %>% pull()

covidNarrowId <- cohorts %>% filter(shinyName == "COVID-19 narrow") %>% select(cohortId) %>% pull()
covidBroadId <- cohorts %>% filter(shinyName == "COVID-19 broad") %>% select(cohortId) %>% pull()

pnaId <- cohorts %>% filter(shinyName == "Pneumonia") %>% select(cohortId) %>% pull()
adverseId <- cohorts %>% filter(shinyName == "Adverse event") %>% select(cohortId) %>% pull()

prettyNames <- data.frame(
  cohortId = c(aceMonoId, arbMonoId, aceArbMonoId, ccbMonoId, thzMonoId, ccbThzMonoId,
               aceComboId, arbComboId, aceArbComboId, ccbComboId, thzComboId, ccbThzComboId),
  cohortName = c("ACE", "ARB", "ACE/ARB", "CCB", "THZ", "CCB/THZ",
                 "ACE+", "ARB+", "ACE/ARB+", "CCB+", "THZ+", "CCB/THZ+"))

primaryAnalysisId <- 5 # Full stratified PS
```


# Sample sizes, total follow-up times and events

## PS Stratification

```{r, echo=FALSE, warning=FALSE, message=FALSE}

sidiapDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/SIDIAP"
cuimcDir <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors/CUIMC"

studyFolder <- "/Users/msuchard/Dropbox/Projects/Covid19EstimationRasInhibitors"

dataFolder <- file.path(sidiapDir, "shinyData")
databaseId <- "SIDIAP"

makeSampleSizeTable <- function(databaseId, 
                                dataFolder,
                                databaseOrder = 1,
                                thisOutcomeId) {
  cmResults <- readRDS(file = file.path(dataFolder, paste0("cohort_method_result_", databaseId, ".rds")))
  colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))
  alpha <- 0.05
  power <- 0.8
  z1MinAlpha <- qnorm(1 - alpha/2)
  zBeta <- -qnorm(1 - power)
  pA <- cmResults$targetSubjects/(cmResults$targetSubjects + cmResults$comparatorSubjects)
  pB <- 1 - pA
  totalEvents <- abs(cmResults$targetOutcomes) + (cmResults$comparatorOutcomes)
  cmResults$mdrr <- exp(sqrt((zBeta + z1MinAlpha)^2/(totalEvents * pA * pB)))
  cmResults$targetYears <- cmResults$targetDays/365.25
  cmResults$comparatorYears <- cmResults$comparatorDays/365.25
  
  cmResults <- cmResults %>% filter(analysisId == primaryAnalysisId, outcomeId == thisOutcomeId)
  
  table <- rbind(
    cmResults %>% filter(targetId == aceArbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "CCB/THZ (m)", order = 1),
    cmResults %>% filter(targetId == aceArbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "CCB/THZ (c)", order = 2),
    
    cmResults %>% filter(targetId == aceArbMonoId, comparatorId == ccbMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "CCB (m)", order = 3),
    cmResults %>% filter(targetId == aceArbComboId, comparatorId == ccbComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "CCB (c)", order = 4),    
    
    cmResults %>% filter(targetId == aceArbMonoId, comparatorId == thzMonoId) %>% mutate(targetId = "ACE/ARB (m)", comparatorId = "THZ (m)", order = 5),
    cmResults %>% filter(targetId == aceArbComboId, comparatorId == thzComboId) %>% mutate(targetId = "ACE/ARB (c)", comparatorId = "THZ (c)", order = 6),    
    
    cmResults %>% filter(targetId == aceMonoId, comparatorId == arbMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "ARB (m)", order = 7),
    cmResults %>% filter(targetId == aceComboId, comparatorId == arbComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "ARB (c)", order = 8),
    
    cmResults %>% filter(targetId == aceMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "CCB/THZ (m)", order = 9),
    cmResults %>% filter(targetId == aceComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "CCB/THZ (c)", order = 10),
    
    cmResults %>% filter(targetId == aceMonoId, comparatorId == ccbMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "CCB (m)", order = 11),
    cmResults %>% filter(targetId == aceComboId, comparatorId == ccbComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "CCB (c)", order = 12),
    
    cmResults %>% filter(targetId == aceMonoId, comparatorId == thzMonoId) %>% mutate(targetId = "ACE (m)", comparatorId = "THZ (m)", order = 13),
    cmResults %>% filter(targetId == aceComboId, comparatorId == thzComboId) %>% mutate(targetId = "ACE (c)", comparatorId = "THZ (c)", order = 14),

    cmResults %>% filter(targetId == arbMonoId, comparatorId == ccbThzMonoId) %>% mutate(targetId = "ARB (m)", comparatorId = "CCB/THZ (m)", order = 15),
    cmResults %>% filter(targetId == arbComboId, comparatorId == ccbThzComboId) %>% mutate(targetId = "ARB (c)", comparatorId = "CCB/THZ (c)", order = 16),
    
    cmResults %>% filter(targetId == arbMonoId, comparatorId == ccbMonoId) %>% mutate(targetId = "ARB (m)", comparatorId = "CCB (m)", order = 17),
    cmResults %>% filter(targetId == arbComboId, comparatorId == ccbComboId) %>% mutate(targetId = "ARB (c)", comparatorId = "CCB (c)", order = 18),
    
    cmResults %>% filter(targetId == arbMonoId, comparatorId == thzMonoId) %>% mutate(targetId = "ARB (m)", comparatorId = "THZ (m)", order = 19),
    cmResults %>% filter(targetId == arbComboId, comparatorId == thzComboId) %>% mutate(targetId = "ARB (c)", comparatorId = "THZ (c)", order = 20)
    
  ) %>% mutate (databaseId = databaseId, databaseOrder = databaseOrder) %>% 
    select(targetId, comparatorId, databaseId, targetSubjects, comparatorSubjects, targetYears, comparatorYears, targetOutcomes, comparatorOutcomes, mdrr, order, databaseOrder)
  
  table$targetSubjects <- formatC(table$targetSubjects, big.mark = ",", format = "d")
  table$comparatorSubjects <- formatC(table$comparatorSubjects, big.mark = ",", format = "d")
  table$targetYears <- formatC(table$targetYears, big.mark = ",", format = "d")
  table$comparatorYears <- formatC(table$comparatorYears, big.mark = ",", format = "d")
  table$targetOutcomes <- formatC(table$targetOutcomes, big.mark = ",", format = "d")
  table$comparatorOutcomes <- formatC(table$comparatorOutcomes, big.mark = ",", format = "d")
  # table$targetIr <- sprintf("%.2f", table$targetIr)
  # table$comparatorIr <- sprintf("%.2f", table$comparatorIr)
  table$mdrr <- sprintf("%.2f", table$mdrr)
  table$targetSubjects <- gsub("^-", "<", table$targetSubjects)
  table$comparatorSubjects <- gsub("^-", "<", table$comparatorSubjects)
  table$targetOutcomes <- gsub("^-", "<", table$targetOutcomes)
  table$comparatorOutcomes <- gsub("^-", "<", table$comparatorOutcomes)
  # table$targetIr <- gsub("^-", "<", table$targetIr)
  # table$comparatorIr <- gsub("^-", "<", table$comparatorIr)
  return(table)
}

# tableSidiap <- makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), databaseOrder = 1, thisOutcomeId = covidNarrowId)
# tableCuimc <- makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), databaseOrder = 2)

tableNarrow <- rbind(
  makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), 
                      databaseOrder = 1, thisOutcomeId = covidNarrowId),
  makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), 
                      databaseOrder = 2, thisOutcomeId = covidNarrowId)
  ) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)

tableBroad <- rbind(
  makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), 
                      databaseOrder = 1, thisOutcomeId = covidBroadId),
  makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), 
                      databaseOrder = 2, thisOutcomeId = covidBroadId)
  ) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)

tablePna <- rbind(
  makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), 
                      databaseOrder = 1, thisOutcomeId = pnaId),
  makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), 
                      databaseOrder = 2, thisOutcomeId = pnaId)
  ) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)

tableAdverse <- rbind(
  makeSampleSizeTable(databaseId = "SIDIAP", dataFolder = file.path(sidiapDir, "shinyData"), 
                      databaseOrder = 1, thisOutcomeId = adverseId),
  makeSampleSizeTable(databaseId = "CUIMC", dataFolder = file.path(cuimcDir, "shinyData"), 
                      databaseOrder = 2, thisOutcomeId = adverseId)
  ) %>% arrange(order, databaseOrder) %>% 
  mutate(targetId = "", comparatorId = "") %>% select(-order, -databaseOrder)
```

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 narrow definition outcomes for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \tiny
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(tableNarrow, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38)),
        command = c(
          "                       \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",     
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",            
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs ARB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",          
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
                    "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}  

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 broad definition outcomes for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \tiny
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(tableBroad, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38)),
        command = c(
          "                       \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",     
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",            
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs ARB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",          
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
                    "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}  

\begin{table}[H]
 \caption{Population size, total exposure time and pneunomia outcomes for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \tiny
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(tablePna, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38)),
        command = c(
          "                       \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",     
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",            
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs ARB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",          
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
                    "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}  

\begin{table}[H]
 \caption{Population size, total exposure time and COVID-19 adverse definition outcomes for ACEI, ARB and CCB/THZ monotherapy and in-combination user target (T) and comparator (C) cohorts.}
  \rowcolors{2}{gray!6}{white}
  \tiny
  \centering{
  \begin{tabular}{p{-2em}p{-2em}rrrrrrrr}
    \hiderowcolors
    \toprule
    &  &  & \multicolumn{2}{c}{Patients} & \multicolumn{2}{c}{Time (years)} & \multicolumn{2}{c}{Events} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
    &  &
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C}
    & \multicolumn{1}{c}{T} & \multicolumn{1}{c}{C} 
    & MDRR \\
    \midrule \showrowcolors
```{r, echo=FALSE, results="asis"}
print(xtable(tableAdverse, format = "latex"),
      include.rownames = FALSE,
      include.colnames = FALSE,
      hline.after = NULL,
      only.contents = TRUE,
      add.to.row = list(
        pos = as.list(c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38)),
        command = c(
          "                       \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",     
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE/ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",            
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs ARB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ACE vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",          
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB/THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
          "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs CCB}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\",
          
                    "\\rowcolor{white} \\\\ \\multicolumn{9}{l}{\\textbf{ARB vs THZ}} \\\\ & \\multicolumn{9}{l}{Monotherapy}  \\\\",
          "                        & \\multicolumn{8}{l}{+ Combination} \\\\"
          )
      ),
      sanitize.text.function = identity)
```
  \bottomrule
  \end{tabular}
  }
\end{table}  


```{r, echo=FALSE}
source(system.file("shiny", "EvidenceExplorer", "PlotsAndTables.R",
                   package = "Covid19IncidenceRasInhibitors"))
# source(system.file("shiny", "EvidenceExplorer", "DataPulls.R",
#                    package = "Covid19IncidenceRasInhibitors"))
```

## PS Stratification

```{r, echo=FALSE, results="asis", cache=FALSE, warning=FALSE}

getCovariateBalance <- function(connection,
                                targetId,
                                comparatorId,
                                databaseId,
                                analysisId,
                                covariate,
                                dataFolder,
                                outcomeId = NULL) {
  file <- sprintf("covariate_balance_t%s_c%s_%s.rds", targetId, comparatorId, databaseId)
  balance <- readRDS(file.path(dataFolder, file))
  colnames(balance) <- SqlRender::snakeCaseToCamelCase(colnames(balance))
  balance <- balance[balance$analysisId == analysisId & balance$outcomeId == outcomeId, ]
  balance <- merge(balance, covariate[covariate$databaseId == databaseId & covariate$analysisId == analysisId, 
                                      c("covariateId", "covariateAnalysisId", "covariateName")])
  balance <- balance[ c("covariateId",
                        "covariateName",
                        "covariateAnalysisId", 
                        "targetMeanBefore", 
                        "comparatorMeanBefore", 
                        "stdDiffBefore", 
                        "targetMeanAfter", 
                        "comparatorMeanAfter",
                        "stdDiffAfter")]
  colnames(balance) <- c("covariateId",
                         "covariateName",
                         "analysisId",
                         "beforeMatchingMeanTreated",
                         "beforeMatchingMeanComparator",
                         "beforeMatchingStdDiff",
                         "afterMatchingMeanTreated",
                         "afterMatchingMeanComparator",
                         "afterMatchingStdDiff")
  balance$absBeforeMatchingStdDiff <- abs(balance$beforeMatchingStdDiff)
  balance$absAfterMatchingStdDiff <- abs(balance$afterMatchingStdDiff)
  return(balance)
}


makeCharacteristicsTable <- function(databaseId,
                                     targetId,
                                     comparatorId,
                                     dataFolder,
                                     outcomeId = covidNarrowId) {

covariate <- readRDS(file.path(dataFolder, paste0("covariate_", databaseId, ".rds")))
colnames(covariate) <- SqlRender::snakeCaseToCamelCase(colnames(covariate))

balance <- getCovariateBalance(NULL, targetId, comparatorId, databaseId = databaseId, analysisId = primaryAnalysisId, outcomeId = outcomeId, 
                               covariate = covariate, dataFolder = dataFolder)



#out <- lapply(balances_strat, function(tmp) {

  scale <- 0.55
  header <- readr::read_file("Table1Top.tex")
  # targetName <- (firstLineClasses %>% filter(cohortId == tmp$targetId))$shortName
  # comparatorName <- (firstLineClasses %>% filter(cohortId == tmp$comparatorId))$shortName

  # if (!(targetName == "THZ" && comparatorName == "ACEi")) {

  targetName <- cohorts %>% filter(cohortId == targetId) %>% select(shinyName) %>% pull
  comparatorName <- cohorts %>% filter(cohortId == comparatorId) %>% select(shinyName) %>% pull
  title <- sub(pattern = "Patient demographics",
               replacement = paste0("Baseline patient characteristcs for ", targetName," (T) and ", comparatorName, " (C) prevalent-users in the ", databaseId, " data source"),
               x = header)

  title <- sub("0.5\\\\textwidth", paste0(scale, "\\\\textwidth"), x = title)
  title <- sub("-0.5em", "+0.5em", x = title)

  title <- sub("% Extra row",
               paste0("& \\\\multicolumn{3}{c}{$N$ = XXX} & \\\\multicolumn{3}{c}{$N$ = XXX} \\\\\\\\"),
               # , "\\\\\\\\ \n",
               #        "\& \\\\multicolumn{3}{c}{Before stratification} \& \\\\multicolumn{3}{c}{After stratification} "),
               x = title)
  
  # if (targetName == "THZ" && comparatorName == "ARB") {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat*", title)
  # } else {
  #   title <- sub("table}", "table}[H]\\\\ContinuedFloat", title)
  # }

  cat(title)

  # table <- prepareTable1(tmp$balance, pathToCsv = file.path("..", "Table1Specs.csv"))
  table <- prepareTable1(balance,pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv", 
                                      package = "Covid19IncidenceRasInhibitors"))
  table <- table[3:nrow(table),]

  print(xtable(table, format = "latex", align = c("l","l","r","r","r","r","r","r")),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE,
        add.to.row = list(pos = list(nrow(table)), command = c("\\bottomrule")),
        sanitize.text.function = identity)

  footer <- readr::read_file("Table1Botton.tex")
  cat(footer)
}
```

```{r, echo=FALSE, results="asis", cache=FALSE, warning=FALSE}

makeAll <- function(db, dbDir) {
  makeCharacteristicsTable(aceArbMonoId, ccbThzMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceArbComboId, ccbThzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceArbMonoId, ccbMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceArbComboId, ccbComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceArbMonoId, thzMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceArbComboId, thzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceMonoId, arbMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceComboId, arbComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceMonoId, ccbThzMonoId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceComboId, ccbThzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceMonoId, ccbMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceComboId, ccbComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(aceMonoId, thzMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(aceComboId, thzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(arbMonoId, ccbThzMonoId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(arbComboId, ccbThzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(arbMonoId, ccbMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(arbComboId, ccbComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  
  makeCharacteristicsTable(arbMonoId, thzMonoId,   databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
  makeCharacteristicsTable(arbComboId, thzComboId, databaseId = db, dataFolder = file.path(dbDir, "shinyData"))
}

makeAll("SIDIAP", sidiapDir)

makeAll("CUIMC", cuimcDir)
```


```{r}

  # }

  # plot <- plotCovariateBalanceScatterPlot(tmp$balance, labels = FALSE,
  #                                         beforeLabel = "Before stratification", afterLabel = "After stratification")
  #                                         # beforeLabel = "", afterLabel = "")
  #   suppressMessages(ggplot2::ggsave(paste0("scatter_", targetName, "_", comparatorName, ".pdf"), plot,
  #                                    width = 3, height = 3, units = "in"))
# })

# text <- prepareTable1(balance,
#               output = "latex",
#               pathToCsv = system.file("shiny", "EvidenceExplorer", "Table1Specs.csv", 
#                                       package = "Covid19IncidenceRasInhibitors"))


# function(balance,
#                           beforeLabel = "Before stratification",
#                           afterLabel = "After stratification",
#                           targetLabel = "Target",
#                           comparatorLabel = "Comparator",
#                           percentDigits = 1,
#                           stdDiffDigits = 2,
#                           output = "latex",
#                           pathToCsv = "Table1Specs.csv") {

```

<!-- ```{r} -->
<!-- knitr::kable(tab, -->
<!--              format = "latex", escape = FALSE, longtable = TRUE, booktabs = TRUE, -->
<!--              caption = "\\textbf{Patient counts, total exposure and COVID-19 diagnoses}. We report study statistics (to change) for both monotherapy and in-combination cohort." -->
<!--              ) %>% -->
<!--   # kableExtra::column_spec(1, width="2cm") %>% -->
<!--   # kableExtra::column_spec(2, width="10cm") %>% -->
<!--   # kableExtra::column_spec(3, width="3cm") %>% -->
<!--   kableExtra::kable_styling(latex_options = "striped") -->
<!-- ``` -->

# Effect estimates

```{r setupOutcomeTables, echo=FALSE}

tcs <- list(
  list(aceArbMonoId, ccbThzMonoId),
  list(aceArbComboId, ccbThzComboId),
  
  list(aceArbMonoId, ccbMonoId),
  list(aceArbComboId, ccbComboId),
  
  list(aceArbMonoId, thzMonoId),
  list(aceArbComboId, thzComboId),
  
  list(aceMonoId, arbMonoId),
  list(aceComboId, arbComboId),
  
  list(aceMonoId, ccbThzMonoId),
  list(aceComboId, ccbThzComboId),
  
  list(aceMonoId, ccbMonoId),
  list(aceComboId, ccbComboId),
  
  list(aceMonoId, thzMonoId),
  list(aceComboId, thzComboId),
  
  list(arbMonoId, ccbThzMonoId),
  list(arbComboId, ccbThzComboId),
  
  list(arbMonoId, ccbMonoId),
  list(arbComboId, ccbComboId),
  
  list(arbMonoId, thzMonoId),
  list(arbComboId, thzComboId)
)
tcs <- lapply(tcs, function(x) { names(x) <- c("targetId", "comparatorId"); return(x) })

makeEffectTable <- function(outcomeName, designName, databaseName, table) {
  header <- readr::read_file("SupTabEffectTop.tex")
  header <- sub(pattern = "OUTCOME", replacement = outcomeName, x = header)
  header <- sub(pattern = "DESIGN", replacement = designName, x = header)
  header <- sub(pattern = "DATASOURCE", replacement = databaseName, x = header)
  cat(header)
  print(xtable(table %>% select(-outcomeId, -analysisId), 
               format = "latex"),
        include.rownames = FALSE,
        include.colnames = FALSE,
        hline.after = NULL,
        only.contents = TRUE,
        sanitize.text.function = identity)
  footer <- readr::read_file("SupTabEffectBottom.tex")
  cat(footer)
}
```

## PS Stratification

### SIDIAP

```{r, echo=FALSE}
databaseId <- "SIDIAP"

outcomesOfInterest <- Covid19IncidenceRasInhibitors:::getOutcomesOfInterest()
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))

sidiapTable <- do.call(
  "rbind",
  lapply(tcs, function(tc) {
    cmResults %>% filter(targetId == tc$targetId, comparatorId == tc$comparatorId) %>%
      left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
      left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
      mutate(ci = sprintf("(%1.2f - %1.2f)", ci95Lb, ci95Ub),
             calibratedCi = sprintf("(%1.2f - %1.2f)", calibratedCi95Lb, calibratedCi95Ub)) %>%
      select(targetName, comparatorName, outcomeId, analysisId,
             rr, ci, p, 
             calibratedRr, calibratedCi, calibratedP)
  }))


databaseId <- "CUIMC"

outcomesOfInterest <- Covid19IncidenceRasInhibitors:::getOutcomesOfInterest()
cmResults <- readRDS(file.path(studyFolder, databaseId, "shinyData", sprintf("cohort_method_result_%s.rds", databaseId)))
colnames(cmResults) <- SqlRender::snakeCaseToCamelCase(colnames(cmResults))

cuimcTable <- do.call(
  "rbind",
  lapply(tcs, function(tc) {
    cmResults %>% filter(targetId == tc$targetId, comparatorId == tc$comparatorId) %>%
      left_join(prettyNames, by = c("targetId" = "cohortId")) %>% rename(targetName = cohortName) %>%
      left_join(prettyNames, by = c("comparatorId" = "cohortId")) %>% rename(comparatorName = cohortName) %>%
      mutate(ci = sprintf("(%1.2f - %1.2f)", ci95Lb, ci95Ub),
             calibratedCi = sprintf("(%1.2f - %1.2f)", calibratedCi95Lb, calibratedCi95Ub)) %>%
      select(targetName, comparatorName, outcomeId, analysisId,
             rr, ci, p, 
             calibratedRr, calibratedCi, calibratedP)
  }))
```

```{r, echo=FALSE, results="asis"}
makeEffectTable("COVID-19 diagnosis", "stratified", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == covidNarrowId, analysisId == primaryAnalysisId))
  
makeEffectTable("COVID-19 hospitalization", "stratifed", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == covidBroadId, analysisId == primaryAnalysisId))

makeEffectTable("intensive services", "stratifed", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == adverseId, analysisId == primaryAnalysisId))

makeEffectTable("pneumonia", "stratifed", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == pnaId, analysisId == primaryAnalysisId))
```

### CUIMC

```{r, echo=FALSE, results="asis"}
makeEffectTable("COVID-19 diagnosis", "stratified", "CUIMC", 
                cuimcTable %>% filter(outcomeId == covidNarrowId, analysisId == primaryAnalysisId))
  
makeEffectTable("COVID-19 hospitalization", "stratifed", "CUIMC", 
                cuimcTable %>% filter(outcomeId == covidBroadId, analysisId == primaryAnalysisId))

makeEffectTable("intensive services", "stratifed", "CUIMC", 
                cuimcTable %>% filter(outcomeId == adverseId, analysisId == primaryAnalysisId))

makeEffectTable("pneumonia", "stratifed", "CUIMC", 
                cuimcTable %>% filter(outcomeId == pnaId, analysisId == primaryAnalysisId))
```

## PS Matching

### SIDIAP

```{r, echo=FALSE, results="asis"}
makeEffectTable("COVID-19 diagnosis", "matched", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == covidNarrowId, analysisId == 6))
  
makeEffectTable("COVID-19 hospitalization", "matched", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == covidBroadId, analysisId == 6))

makeEffectTable("intensive services", "matched", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == adverseId, analysisId == 6))

makeEffectTable("pneumonia", "matched", "SIDIAP", 
                sidiapTable %>% filter(outcomeId == pnaId, analysisId == 6))
```

### CUIMC

```{r, echo=FALSE, results="asis"}
makeEffectTable("COVID-19 diagnosis", "matched", "CUIMC", 
                cuimcTable %>% filter(outcomeId == covidNarrowId, analysisId == 6))
  
makeEffectTable("COVID-19 hospitalization", "matched", "CUIMC", 
                cuimcTable %>% filter(outcomeId == covidBroadId, analysisId == 6))

makeEffectTable("intensive services", "matched", "CUIMC", 
                cuimcTable %>% filter(outcomeId == adverseId, analysisId == 6))

makeEffectTable("pneumonia", "matched", "CUIMC", 
                cuimcTable %>% filter(outcomeId == pnaId, analysisId == 6))
```
